Descriptive Results

### 2024-11-25 draftdata.Rmd
descriptivescontd

Histogram: overall gender distribution in sample

```{r histogram gender, echo=FALSE}
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

Genders per department (0 = female, 1 = male)

```{r gender per dep., echo=FALSE}

# Wave 1: Gender count per department 
table(df_ego$discipline.24, df_ego$gender)
```

## H index - Ego level

>>>>

Histogram: overall gender distribution in sample
```{r histogram gender, echo=FALSE}
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

Genders per department (0 = female, 1 = male)
```{r gender per dep., echo=FALSE}
# Wave 1: Gender count per department 
table(df_ego$discipline.24, df_ego$gender)
```

## H-Index - Ego level

### 2024-11-25 draftdesresults.Rmd
ypagenorespond
descriptivescontd

</html>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r clean, hide =TRUE}
rm(list = ls())
```

@@

```{r package, hide=TRUE, results='hide'}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

```{r functions 1, hide =TRUE, results = 'hide' }
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

More functions

```{r functions 2, hide=TRUE, results ='hide'}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving scholar output}
# save the output of your function

@@

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

```{r matrix data ego}

@@

# Network Description

@@

```{r nodes}
vcount(test_w1)
```

@@

```{r edges}
ecount(test_w1)
```

@@

```{r dyad cen}
igraph::dyad_census(test_w1)
```

@@

```{r triad cen}
igraph::triad_census(test_w1)
```

@@

```{r edge dens}
# edge density
igraph::edge_density(test_w1)
```

@@

Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters. In the context of our dataset, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees). Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper. Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.

```{r degree}
# Calculate degree centrality
degree_testw1 <- degree(test_w1)
degree_testw1 <- as.data.frame(degree_testw1)

@@

```{r betweenness}
# Calculate betweenness centrality
betweenness_w1 <- igraph::betweenness(test_w1, directed = TRUE)
betweenness_w1 <- as.data.frame(betweenness_w1)

@@

```{r}
# Clustering the wave 
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)

@@

## Segregation ?

# Plots

>>>>

</html>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r clean, echo=FALSE}
rm(list = ls())
```

@@

```{r package, hide=TRUE, echo=FALSE}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

```{r functions 1, echo=FALSE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

More functions
```{r functions 2, echo=FALSE}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

```{r scholar data,echo=FALSE}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

```{r saving scholar output,echo=FALSE}
# save the output of your function

@@

```{r df_ego data,echo=FALSE}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

# Descriptive Analysis

[For Ego-level descriptives on gender and h-index, please consult the latter part of the Data & Analysis part of this final report]

## Network Description

## Making graph object

```{r matrix data ego, echo=FALSE}

@@

@@

```{r nodes, echo=FALSE}
vcount(test_w1)
```

@@

```{r edges, echo=FALSE}
ecount(test_w1)
```

@@

```{r dyad cen, echo=FALSE}
igraph::dyad_census(test_w1)
```

@@

```{r triad cen, echo=FALSE}
igraph::triad_census(test_w1)
```

@@

```{r edge dens, echo=FALSE}
# edge density
igraph::edge_density(test_w1)
```

@@

Degree centrality, often simply called 'degree', measures the number of connections a scholar, or ego, has with other scholars, known as alters. Here, we distinguish between two types of degrees: incoming connections (indegrees) and outgoing connections (outdegrees). Indegrees represent ties directed toward the ego, which in this case signify instances where the ego is **not** the primary author of a paper. Conversely, outdegrees represent ties originating from the ego, indicating collaborations where the ego assumes the role of the first author.

```{r degree, echo=FALSE}
# Calculate degree centrality
degree_testw1 <- degree(test_w1)
degree_testw1 <- as.data.frame(degree_testw1)

@@

```{r betweenness, echo=FALSE}
# Calculate betweenness centrality
betweenness_w1 <- igraph::betweenness(test_w1, directed = TRUE)
betweenness_w1 <- as.data.frame(betweenness_w1)

@@

```{r, echo=FALSE}
# Clustering the wave 
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)

@@

```
## Network Plots
